---
title: "p8105_hw1_yl4359"
author: "Yue Lai"
date: "9/16/2019"
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

Create a data frame comprised of:

* a random sample of size 8 from a standard Normal distribution

* a logical vector indicating whether elements of the sample are greater than 0

* a character vector of length 8

* a factor vector of length 8, with 3 different factor “levels”

```{r}
df_1 = tibble(
  vec_norm = rnorm(8),
  vec_logical = vec_norm > 0,
  vec_char = c("apple","banana", "orange", "pineapple", "cherry", "buleberry", "strawberry", "watermelon"),
  vec_factor = factor(c("dislike", "so so", "so so", "like", "dislike", "like", "like", "like"))
)
```

Convert logical, character and factor variables to numeric variable. 

```{r eval = FALSE}
as.numeric(pull(df_1, vec_logical))
as.numeric(pull(df_1, vec_char))
as.numeric(pull(df_1, vec_factor))
```

In a second code chunk:

* convert the logical vector to numeric, and multiply the random sample by the result

* convert the logical vector to a factor, and multiply the random sample by the result

* convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```{r}
as.numeric(pull(df_1, vec_logical))*pull(df_1, vec_norm)
as.factor(pull(df_1, vec_logical))*pull(df_1, vec_norm)
as.numeric(as.factor(pull(df_1, vec_logical)))*pull(df_1, vec_norm)
```

# Problem 2

Create a data frame comprised of: 

* x: a random sample of size 500 from a standard Normal distribution

* y: a random sample of size 500 from a standard Normal distribution

* A logical vector indicating whether x + y > 1

* A numeric vector created by coercing the above logical vector

* A factor vector created by coercing the above logical vector

```{r} 
df_2 = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logical = (x + y) > 1,
  vec_numeric = as.numeric(vec_logical),
  vec_factor = as.factor(vec_logical)
)
```

* The size of the dataset is `r nrow(df_2)` rows and `r ncol(df_2)` columns. 

* The mean of x is `r mean(pull(df_2, x))`.

* The median of x is `r median (pull(df_2, x))`.

* The standard deviation of x is `r sd(pull(df_2, x))`.

* The proportion of cases for which x + y > 1 is `r sum(pull(df_2, vec_logical))/500`.

Make a scatterplot of y vs x; color points using the logical variable. Make a second and third scatterplot that color points using the numeric and factor variables, respectively, and comment on the color scales. 

Export the first scatterplot to the project directory.

```{r yx_scatter}
ggplot(df_2, aes(x = x, y = y, color = pull(df_2, vec_logical))) + geom_point()
ggsave("hw1_plot", device = "jpeg", path =  "C:/Users/16462/Documents/Columbia/P8105/Homework/p8105_hw1_yl4359")
ggplot(df_2, aes(x = x, y = y, color = pull(df_2, vec_numeric))) + geom_point()
ggplot(df_2, aes(x = x, y = y, color = pull(df_2, vec_factor))) + geom_point()
```
